---
title: '2501967096_MidExam'
author: "Ryan Bertrand"
date: '2022-04-02'
output: html_document
---


##### **1. Apply the following exploratory data analysis techniques using R on `CarPrice` dataset: (25 pts.)**

a.	Using `mfrow` parameter, construct a two-by-two plot array showing the concentrations of the following four attributes versus the record number in the dataset: 

(1) Wheelbase, top left; 
(2) carwidth, top right; 
(3) fueltype, lower left; and 
(4) CylinderNumber, lower right. 

In all cases, the x-axis label should read `Record number in dataset` and the y-axis should read the attribute. 
Each plot should have a title spelling out the name of the element on which the attribute is based (e.g., “wheelbase” for the top-left plot).
```{r}
data<- read.csv(file = 'CarPrice-EvenSID.csv')
#View(data)
par(mfrow=c(2,2))
data$row_num <- seq.int(nrow(data)) 
data$FuelType <- as.factor(data$FuelType)
data[data$CylinderNumber=="two",]$CylinderNumber<-2
data[data$CylinderNumber=="three",]$CylinderNumber<-3
data[data$CylinderNumber=="four",]$CylinderNumber<-4
data[data$CylinderNumber=="five",]$CylinderNumber<-5
data[data$CylinderNumber=="six",]$CylinderNumber<-6
data[data$CylinderNumber=="eight",]$CylinderNumber<-8
data[data$CylinderNumber=="twelve",]$CylinderNumber<-12
plot(data$row_num, data$WheelBase, xlab="index", ylab="wheel base")
title("Wheel Base")
plot(data$row_num, data$CarWidth, xlab="index", ylab="car width")
title("Car Width")
plot(data$row_num, data$FuelType, xlab="index", ylab="fuel type", yaxt="n")
axis(2, at = seq(1,2,1), labels = levels(data$FuelType))
title("Fuel Type")
plot(data$row_num, data$CylinderNumber, xlab="index", ylab="cylinder number")
title("Cylinder Number")
```

```
__Write your explanation here:__
Plot di atas menjelaskan bahwa:
* Panjang wheel base pada mobil yaitu mulai dari 86,6 inch sampai dengan 120,9 inch tetapi rata-rata wheel base yang digunakan oleh mobil yaitu 90-100 inch
* Lebar mobil pada mobil yaitu mulai dari 60 inch sampai dengan 72 inch tetapi rata-rata lebar mobil yang digunakan pada mobil yaitu 64-69 inch
* Bahan bakar yang digunakan oleh mobil yaitu gas dan diesel, tetapi hampir semua mobil memakai bahan bakar gas dan sisanya memakai diesel
* Mobil memiliki 7 macam silinder: 2 silinder, 3 silinder, 4 silinder, 5 silinder, 6 silinder, 8 silinder ,dan 12 silinder, tetapi kebanyakan mobil memakai 4 silender
```

 b.	Construct a mosaic plot showing the relationship between the variables `Carbody` and `CylinderNumber` in the `CarPrice` data frame. Does this plot suggest a relationship between these variables? Explain your answer.
```{r}
#write your code here
MosaicPlot <-table(data$CarBody,data$CylinderNumber)
mosaicplot(MosaicPlot)
```

```
__Write your explanation here:__
Dari mosaic plot diatas dapat disimpulkan bahwa:
* Tipe mobil convertible tidak memiliki mesin yang bersilinder 2, 3, 5, dan 12, tetapi memiliki mesin bersilinder 4, 6, dan 8
* Tipe mobil hardtop tidak memiliki mesin yang bersilinder 2, 3, dan 12, tetapi memiliki mesin bersilinder 4, 5, 6 ,dan 8
* Tipe mobil hatchback hanya tidak memiliki mesin yang bersilinder 12, tetapi memiliki mesin bersilinder 2, 3, 4, 5, 6, dan 8
* Tipe mobil sedan tidak memiliki mesin yang bersilinder 2 dan 3, tetapi memiliki mesin bersilinder 4, 5, 6, 8, dan 12
* Tipe mobil wagon tidak memiliki mesin yang bersilinder 2, 3, 8, dan 12, tetapi memiliki mesin bersilinder 4, 5, dan 6
* Dari semua tipe mobil mesin 4 silinder adalah mesin yang paling banyak untuk dipakai
```

c.	Compute the correlation for all attributes. Interpret the statistical findings!
```{r}
#write your code here
library(Hmisc)
dataAngka <- data[,c("WheelBase","CarWidth","CurbWeight","CylinderNumber","HorsePower","Citympg","Price")]
rcorr(as.matrix(dataAngka), type = "spearman")
```

```
__Write your explanation here:__
Dari data di atas kita dapat mengetahui korelasi yang paling tinggi yaitu antara Price dengan CurbWeight yaitu nilainya 0.91
```

##### **2. You need to compare three ways (three-sigma edit rule, Hampel identifier, boxplot rule) of detecting univariate outliers for the `wheelbase` attribute from the data frame: (20 pts.)**

a.	Generate a plot for each technique and give the appropriate features (labels, line type, etc.). Based on these plots, which outlier detector seems to be giving the more reasonable results?
```{r}
#write your code here
ThreeSigma <- function(x, t = 3){

   mu <- mean(x, na.rm = TRUE)
   sig <- sd(x, na.rm = TRUE)
   if (sig == 0){
      message("All non-missing x-values are identical")
   }
  up <- mu + t * sig
  down <- mu - t * sig
  out <- list(up = up, down = down)
  return(out)
}

Hampel <- function(x, t = 3){

   mu <- median(x, na.rm = TRUE)
   sig <- mad(x, na.rm = TRUE)
   if (sig == 0){
        message("Hampel identifer implosion: MAD scale estimate is zero")
   }
   up <- mu + t * sig
   down <- mu - t * sig
   out <- list(up = up, down = down)
   return(out)
}
   
BoxplotRule<- function(x, t = 1.5){

 xL <- quantile(x, na.rm = TRUE, probs = 0.25, names = FALSE)
 xU <- quantile(x, na.rm = TRUE, probs = 0.75, names = FALSE)
 Q <- xU - xL
 if (Q == 0){
 message("Boxplot rule implosion: interquartile distance is zero")
 }
 up <- xU + t * Q
 down <- xU - t * Q
 out <- list(up = up, down = down)
 return(out)
}   

ExtractDetails <- function(x, down, up){

 outClass <- rep("N", length(x))
 indexLo <- which(x < down)
 indexHi <- which(x > up)
 outClass[indexLo] <- "L"
 outClass[indexHi] <- "U"
 index <- union(indexLo, indexHi)
 values <- x[index]
 outClass <- outClass[index]
 nOut <- length(index)
 outList <- list(nOut = nOut, lowLim = down,
 upLim = up,index = index,
 values = values,
 outClass = outClass)
 return(outList)
}


FindOutliers <- function(x, t3 = 3, tH = 3, tb = 1.5){
 threeLims <- ThreeSigma(x, t = t3)
 HampLims <- Hampel(x, t = tH)
 boxLims <- BoxplotRule(x, t = tb)

 n <- length(x)
 nMiss <- length(which(is.na(x)))

 threeList <- ExtractDetails(x, threeLims$down, threeLims$up)
 HampList <- ExtractDetails(x, HampLims$down, HampLims$up)
 boxList <- ExtractDetails(x, boxLims$down, boxLims$up)

 sumFrame <- data.frame(method = "ThreeSigma", n = n,
 nOut = threeList$nOut,
 lowLim = threeList$lowLim,
 upLim = threeList$upLim)
 
 upFrame <- data.frame(method = "Hampel", n = n,
 nOut = HampList$nOut,
 lowLim = HampList$lowLim,
 upLim = HampList$upLim)
 
 sumFrame <- rbind.data.frame(sumFrame, upFrame)
 
 upFrame <- data.frame(method = "BoxplotRule", n = n,
 nOut = boxList$nOut,
 lowLim = boxList$lowLim,
 upLim = boxList$upLim)
 
 sumFrame <- rbind.data.frame(sumFrame, upFrame)

 threeFrame <- data.frame(index = threeList$index,
 values = threeList$values,
 type = threeList$outClass)
 HampFrame <- data.frame(index = HampList$index,
 values = HampList$values,
 type = HampList$outClass)
 boxFrame <- data.frame(index = boxList$index,
 values = boxList$values,
 type = boxList$outClass)
 outList <- list(summary = sumFrame, threeSigma = threeFrame,
 Hampel = HampFrame, boxplotRule = boxFrame)
 return(outList)
}
```

```{r}
fullSummary <- FindOutliers(data$WheelBase)
plot(data$WheelBase,ylim=c(80,125),xlim=c(0,200))
title("three sigma with low and high limit")
axis(1, at=seq(0,200,25))
axis(2, at=seq(80,120,5))
lowlim3s <-fullSummary$summary[1 , 4]
highlim3s <-fullSummary$summary[1 , 5]
abline(h = lowlim3s, col="green") 
abline(h = highlim3s, col="red")

plot(data$WheelBase,ylim=c(80,125),xlim=c(0,200))
title("hample with low and high limit")
axis(1, at=seq(0,200,25))
axis(2, at=seq(80,120,5))
lowlimh <-fullSummary$summary[2 , 4]
highlimh <-fullSummary$summary[2 , 5]
abline(h = lowlimh, col="green") 
abline(h = highlimh, col="red")

plot(data$WheelBase,ylim=c(80,125),xlim=c(0,200))
title("bloxplot rule with low and high limit")
axis(1, at=seq(0,200,25))
axis(2, at=seq(80,120,5))
lowlimb <-fullSummary$summary[3 , 4]
highlimb <-fullSummary$summary[3 , 5]
abline(h = lowlimb, col="green") 
abline(h = highlimb, col="red")

#lowlim3s -> untuk mengetahui lower limit dari three sigma
#highlim3s -> untuk mengetahui higher limit dari three sigma
#lowlimh -> untuk mengetahui lower limit dari hample
#highlimh -> untuk mengetahui higher limit dari hample
#lowlimb -> untuk mengetahui lower limit dari boxplot rule
#highlimb -> untuk mengetahui higher limit dari boxplotrule
```

```
__Write your explanation here:__ #blm pasti bener explainnya
Dari 3 plot diatas kita dapat mengetahui, jika menggunakan rumus:
* Three Sigma: lower limitnya adalah 80.69126, dan higher limitnya adalah 116.8219
* Hample: lower limitnya adalah 84.99094, dan higher limitnya adalah 109.0091
* Box Plot Rule: lower limitnya adalah 90.55, dan higher limitnya adalah 114.25
```

b.	How many data points are declared outliers by each of the technique? Based on this data points, which outlier detector seems to be giving the more reasonable results?
```{r}
#write your code here
i<-1
while(i <= 3){
  hasil<-paste(fullSummary$summary[i , 1],"=", fullSummary$summary[i , 3])
  i <- i + 1
  print(hasil)
}
```

```
__Write your explanation here:__
Outlier yang dapat ditemukan dengan menggunakan ThreeSigma yaitu hanya 1 outlier, Hample memiliki 18 outlier, dan BoxplotRule memiliki 11 outlier
```

##### **3. Do a comprehensive EDA on your dataset then find the best-fit linear regression model then answer the following questions: (40 pts.)**

a.	Interpret the result of your model.
```{r}
#write your code here
perbandingan <- lm(log(Price)~CurbWeight,data=data)
plot(perbandingan, which=1)
```

```
__Write your explanation here:__
Dari plot ini dapat menentukan apakah kasus-kasus berpengaruh untuk model ini, dan dapat mencari nilai outlying.
```

b.	Write down the equation of the best fitting line.
```{r}
#write your code here
summary(perbandingan)
```

```
__Write your explanation here:__
Dari summary ini kita dapat mengetahui F Statistik meningkat menjadi 783,9 dan memiliki p value yang sangat signifikan
```

c.	Is your model good? Why or why not?
```{r}
#write your code here
library(caret)
set.seed(1)
validation_index <- createDataPartition(data$Price, p=0.8, list = FALSE)
validationset = data[-validation_index,]
validationset$predicted <- predict(perbandingan, validationset)
actualPrediction <- data.frame(validationset$Price, validationset$predicted, validationset$Price - validationset$predicted)
names(actualPrediction) <- c ("Price", "Predicted", "Residuals")
correlationAccuracy <- cor(actualPrediction)
correlationAccuracy
```

```
__Write your explanation here:__
model yang saya buat sudah bagus karena model dari correlation menunjukkan nilai akurasi 86% 
```
d.	Based on your answer in c, will you deploy the model? Why or why not?
```{r}
#write your code here
trainingset = data[validation_index,]
prediction <- predict(perbandingan, validationset)
plot(exp(prediction), validationset$Price, xlab="Predicted Price", ylab="Actual Price")
title("Predicted Price vs Actual Price")
abline(a=0, b=1)
```

```
__Write your explanation here:__
Model yang saya buat sudah baik karena dibuktikan didalam plot "Predicted Price vs Actual Price" hanya ada 1 data yang tidak mendekati garis lainnya mendekati garis semua
```